MachLLensFinder - I: A Machine Learning Strong Lensing Identification Pipeline

### 2016-11-10 ms.tex
added more text to results, particularly in the ROC curve

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\hspace{-20pt}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  Note, fewer pixels per cell will better
  resolve the arc feature.  The brightest lines align with prominent
  edges.}
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Machine Learning Algorithm: Logistic Regression}
%-------------------------------------------------%

@@

%-------------------------------------------------%
\subsection{Effects of Regularization on Model Performance}\label{sec:unregularizedfit}
%-------------------------------------------------%

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization

%-------------------------------------------------%
\subsection{Failed identifications}
%-------------------------------------------------%

@@

Figure~\ref{fig:ROC} shows the \todo{ROC curve for XYZ(???) models,
with the AUC value indicated in the legend.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:ROC}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC.pdf}
\caption{ROC curve for a model trained on the HST-like data with the
  Logistic Regression algorithm.  Here, we use the parameters: CPB=(1,
  1), $N_\text{orien}=9$, PPC=(16, 16), $C_\text{reg}=100.$.  The AUC
  is 0.966.}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]\label{fig:hogvisual}
\begin{center}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or5ppc32cpb1.pdf}\hspace{-20pt}
\includegraphics[width=1\columnwidth]{figures/105_lensed_imgs_1or9ppc16cpb1.pdf}\hspace{-20pt}
\caption{Visualized HOG feature vectors of the sample lensed HST-like
  image from Figure~\ref{fig:mockimages}.  Left: The corresponding HOG
  visualization with N$_\text{orient}=5$, (32, 32) pixels per cell,
  and (1, 1) cells per block.  Right: The HOG visualization of the
  same mock image with N$_\text{orient}=9$, (16, 16) pixels per cell,
  and (1, 1) cells per block.  The brightest lines align with
  prominent edges.  Note, while fewer pixels per cell will better
  resolve the arc feature, the ``edge'' corresponding to the arc is
  less prominent.  }
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Machine Learning Algorithm: Logistic Regression}\label{sec:logreg}
%-------------------------------------------------%

Logisitic regression is a linear classifier, which finds the optimal
hyperplane between two classes of data points.  This hyperplane
defines the optimal model.  We must regularize the model to prevent
overfitting.

In regularization, the goal is to minimize a cost function with
respect to ....  Larger values of $C_\text{LogReg}$ correspond to
increasing model complexity.  Figure~\ref{fig:regularization} shows
the accuracy of a model for selected HOG parameters as a function of
the regularization parameter, $C_\text{LogReg}$.  We plot the
regularization dependency for HOG parameterization of
$N_\text{orient}=9$, $PPC=(16, 16)$, $CPB=(1,1)$.

The accuracy of a model can be defined as either the score of the
model on a test set, or the AUC for the ROC curve.

@@

@@

Figure~\ref{fig:ROC} shows the ROC curves for three different HOG
parameterizations for the HST-like dataset in red, green, and blue.
The parameters and corresponding AUC for each curve are labeled in the
legend.  The models for the HST-like dataset perform well, and have
AUCs very close to 1.  On the other hand, the model for our LSST-like
dataset does not perform well.  The dashed diagonal like corresponds
to a model that is as good as a random classifier, e.g. a coin-flip
for each test image.  The LSST-like ROC curve does marginally better,
and the $AUC=0.527$ is within the statistical noise of the sample.

We train the model corresponding to each curve with the logistic
regression regularization parameter, $C_\text{LogReg}$, that best
describes the training dataset without overfitting.  We discuss the
choice of regularization parameter in
Section~\ref{sec:regularizedfit}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:ROC}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
\caption{Red, green, blue: ROC curves for a models trained on the
  HST-like data with the Logistic Regression algorithm.  The magenta
  shows the ROC curve for the LSST-like data.  The corresponding
  parameters are labeled, N for number of orientations, ppc for
  pixels-per-cell, cpb for cells-per-block, and C for best
  regularization parameter.  }
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Effects of Regularization on Model Performance}\label{sec:regularizedfit}
%-------------------------------------------------%

% Logistic regression and regularization
As described in Section~\ref{sec:logreg}, logistic regression trains a
model with complexity determined by the regularization parameter.  The
regularization parameter ultimately defines the model performance.
Figure~\ref{fig:regularization} shows the model performance as a function of
regularization parameter.

% Scores vs. regularization on larger train/test set with comparable
% grid search in parameterization
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure}[t]\label{fig:regularization}
\begin{center}
\includegraphics[width=\columnwidth]{figures/ROC_multipleHOG.png}
\caption{}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%-------------------------------------------------%
\subsection{Failed identifications}\label{sec:failedids}
%-------------------------------------------------%
